Parallel Adaptive Importance Sampling

### 2016-06-28 PAIS.tex
Final changes + final figure
Final couple of typos and added the posterior distribution figure for
the chemical system section.

% solution to QSSA ode and Gamma noise assumption
\subsubsection{Target Distribution}

We now formalise the posterior of interest. We look for a distribution over the parameter $\mathbf{k} = (k_2, k_3)^T$, given that we know $k_1 = 100$ and $k_4=1$. We generate our data by making ten observations of the system at $t_i = 2, 4, \dots, 20$, here simulated by solving the full system, \eqref{eqn:full_system}, governed by the differential equations
\begin{align*}
	\frac{\text{d}S_1}{\text{d}t} &= k_1 - k_2S_1(t)+k_3S_2(t), \\
	\frac{\text{d}S_2}{\text{d}t} &= k_2S_1(t) - (k_3+k_4)S_2(t),
\end{align*}
with initial conditions $S_1(0)=S_2(0) = 0$, and parameter values $\mathbf{k} = (50, 100)^T$. We then add noise taken from a Gamma distribution with variance $\sigma^2 = 225$ and centred at each $\mathcal{S}(t_i)=S_1(t_i)+S_2(t_i)$.

@@

>>>>

% solution to QSSA ode and Gamma noise assumption
\subsubsection{Target Distribution}\label{sec:345}

We now formalise the posterior of interest. We look for a distribution over the parameter $\mathbf{k} = (k_2, k_3)^T$, given that we know $k_1 = 100$ and $k_4=1$. We generate our data by making ten observations of the system at $t_i = 2, 4, \dots, 20$, here simulated by solving the full system, \eqref{eqn:full_system}, governed by the differential equations
\begin{align*}
	\frac{\text{d}S_1}{\text{d}t} &= k_1 - k_2X_1(t)+k_3X_2(t), \\
	\frac{\text{d}S_2}{\text{d}t} &= k_2X_1(t) - (k_3+k_4)X_2(t),
\end{align*}
with initial conditions $X_1(0)=X_2(0) = 0$, and parameter values $\mathbf{k} = (50, 100)^T$. We then add noise taken from a Gamma distribution with variance $\sigma^2 = 225$ and centred at each $\mathcal{S}(t_i)=X_1(t_i)+X_2(t_i)$.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.65\textwidth]{"figures/C1_posterior"}
\caption{The posterior distribution on the parameters $k_2$ and $k_3$
  given the data and priors described in Section \ref{sec:345}.}
\label{fig:345}
\end{figure}

Figure \ref{fig:345} presents a visualisation of the posterior
distribution for this problem, found by exhaustive MH simulation.
